### 2022-09-27 main/chapter_context.tex
move table; write some philosophy and neutrinos

\subsection{Opportunities for future Standard Models}
Problems with the Standard Model mean it needs replacing with supersymmetry
--- is a false statement.
Such an argument could be tempting to motivate this thesis, but the
Standard Model is actually very good within its domain.
Newton's laws are also very good within theirs \TODO{}

\TODO{Limitations: uncertainties and unknowns}
\TODO{uncertainties: lagrangian form for neutrino masses, mass values (hierarchy, mixing angles); composition of dark matter}
\TODO{unknowns: lack of convincing solutions; unification of gravity with quantum mechanics, origin of structure and parameters of standard model}

\paragraph{Neutrino masses.}
\TODO{Dirac neutrinos, possibly supplemented with a Majorana term}
\TODO{Weinberg operator for Majorana neutrinos}

\TODO{mass models: dirac, Majorana, seesaw~\cite{
wells2020discovery,
king2003neutrino,
thomson2013modern
}}

@@

@@

\TODO{
primordial black holes~\cite{bernard2019primordial},
WIMPs~\cite{jungman1996wimp},
axions~\cite{kim2008axions},
dust?~\cite{garrett2010dark}
}
\TODO{combinations!}

>>>>

\subsection{Opportunities for future Standard Models}
Problems with the Standard Model mean it needs replacing with supersymmetry
--- is currently a false statement.
Such an argument could be tempting to motivate this thesis, but the
Standard Model is actually good in its domain.
This discussion is therefore oriented towards how the Standard Model could do
better where it already works, and how that remit might expand to increase its
generality.

When `nobody knows' the answer to a riddle, the status lies between two
extremes:
many answers appear satisfactory and none is the clear best,
or no satisfactory answer is yet known.
To distinguish these two cases, we choose for them the respective labels
\emph{uncertain} and \emph{unknown}:
the model of neutrino masses is \emph{uncertain},
but the reconciliation quantum field theory with general relativity is
\emph{unknown}.

A problem with the Standard Model is that algorithms to compute its
general consequences
(where perturbative and discrete lattice methods are impractical)
are unknown.
But this is not an opportunity because it is inherent to the framework
(of quantum field theory) that all serious alternatives also use.

Before introducing supersymmetry, this section briefly review some promising
directions of change for futrue models.

\paragraph{Neutrino masses.}
Neutrinos could be Dirac fermions with Yukawa masses and boring right-chiral
fields.
Or they could also have Majorana mass terms, for which the seesaw mechanism
can simultaneously generate the observed light neutrinos and heavy `sterile'
neutrinos.
Or their masses could come from other operators without right-handed
fields~\cite{
thomson2013modern,
chala2021neutrino,
wells2020discovery
}.
This riddle is largely unknown, and new results from theory or experiment
that pinpoint a correct model could improve the Standard Model in the neutrino
domain.

@@

\TODO{gravity}

@@

\TODO{
sterile neutrinos~\cite{boyarsky2019sterile},
primordial black holes~\cite{bernard2019primordial},
WIMPs~\cite{jungman1996wimp},
axions~\cite{kim2008axions},
dust?~\cite{garrett2010dark}
}
\TODO{combinations!}
